Generation of TypeScript Declaration Files from JavaScript Code

### 2020-08-31 programming-2021/main.tex
example packages for literal types

\paragraph*{Literal types vs string}
JavaScript libraries often (?) use literal strings to select
options and configurations. For example, \dots

>>>>

\paragraph*{Literal types vs string}
Many JavaScript libraries use literal strings to select
options and configurations. To be concrete, 1925 DT packages rely on
literal types (see Table~\ref{tab:dts-parse-stats}). For example, the bonjour
package\footnote{\url{https://www.npmjs.com/package/@types/bonjour}}
relies on strings to control events and indicate protocols in (different) interfaces:
\begin{lstlisting}[language=TypeScript]
    removeAllListeners(event?: 'up' | 'down'): this;
    protocol?: 'udp'|'tcp';
\end{lstlisting}
The carlo
package\footnote{\url{https://www.npmjs.com/package/@types/carlo}}
uses it to distinguish different 
types of events.
\begin{lstlisting}[language=TypeScript]
export type AppEvent = 'exit' | 'window';
\end{lstlisting}
% coinbase ...
